Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-16 paper/paper.Rmd

Buffering is mostly applied in the coordinate space.
However, there is no practical limitation that would prevent this method to be applied in a 2D + time setting.
Because \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods.

@@

The "Spatial blocking" from package \pkg{blockCV} comes with various options to customize the zone creation.
Besides the choice of relying on an initial random  (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`) for the final partition aggregation, support for SDM specific background data is built-in.
Supplying a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) will create a quadratic block pattern across the study area.
Ultimately, users can also supply a user-defined polygon via argument `rasterLayer` to define the zones.

After the initial block creation, multiple "blocks" are combined to form a partition, honoring the number of folds requested by the user.
For example, in a five-fold scenario with a grid of four columns and five rows, the method would combine one fifth of all blocks (= four blocks) into a single partition.

>>>>

Buffering is mostly applied in the coordinate space.
However, there is no practical limitation that would prevent this method to be applied in a 2D + time setting.
Since \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods (see Table \@ref(tab:sptcv-methods)).

@@

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
Additionally, the user might supply a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) which will ensure a quadratic block pattern across the study area.
This kind of blocking might be of special interest for SDM studies as well as the possibility to supply a user-defined polygon via argument `rasterLayer` with predefined blocking zones.

After the initial block creation, multiple "blocks" are combined to form a partition in correspondence with the number of folds requested by the user.
For example, in a five-fold scenario with a grid of four columns and five rows, the method would combine one fifth of all blocks (= four blocks) into a single partition.
